---
title:"Data"
output:html_document
---

# About the Data 

The PRAM dataset stands for the Pregnancy Risk Assessment Monitoring System. It collects state-specific data on maternal behaviors/experiences before, during, and after birth.


# Data Cleaning 

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

```{r}


#alcohol_data_2007 =
 # read.csv("~/Desktop/finalproject_p8105/data/PRAM_2007_alcohol.csv")

#tobacco_data_2007 =
 # read.csv("~/Desktop/finalproject_p8105/data/PRAM_2007_tobacco.csv")

alcohol_data_2007 = read_csv("./data/PRAM_2007_alcohol.csv")

tobacco_data_2007 = read_csv("./data/PRAM_2007_alcohol.csv")

contraception_data_2007 = read_csv("./data/PRAM_2007_contraception.csv")
```

Cleaning Alcohol data 

```{r}
cleaned_alc_2007 <- alcohol_data_2007 |>
  janitor::clean_names() |>
  select(-data_value_std_err, -geolocation, -data_value_type)|>
  drop_na(response)

view(cleaned_alc_2007)
```

Cleaning Tobacco Data

```{r}
cleaned_tobac_2007 <- tobacco_data_2007|>
  janitor::clean_names() |>
  select(-data_value_std_err, -geolocation, -data_value_type)|>
  drop_na(response)

view(cleaned_tobac_2007)
```


Cleaning Contraception Data

```{r}
cleaned_contra_2007 <- contraception_data_2007 %>%
  janitor::clean_names() %>%
  select(-data_value_std_err, -geolocation, -data_value_type) %>%
  drop_na(response)

view(cleaned_contra_2007)
```

## Variables 
=======
##Comparing Variables 

```{r}
cleaned_alc_2007 |>
  ggplot(
    aes(x = response, y = break_out_category)
    
  )

cleaned_alc_2007 |>
  ggplot(aes(x = response, y = , group = question, color = as.factor(question))) +
  geom_line() +
  labs(title = "Spaghetti Plot", x = "Timepoint", y = "Value") +
  theme_minimal()


cleaned_alc_2007 |>
  ggplot(aes(x = response, group = question, fill = as.factor(response))) +
  stat_count(position = "dodge") +
  labs(title = "Count of 'Yes' and 'No' Responses", x = "Response", y = "Count") +
  theme_minimal()

questions_df <- cleaned_alc_2007 |>
  data.frame(
    questions = c("Indicator of drinking any alcohol during the past two years")
  )

questions_df |>
  ggplot(aes( x = response, y = question))

  
```



### Alcohol

- `year`  refers to the year data was recorded
- `class` refers to ....
- `topic` refers to the topic of the data
- `question` the question that was recorded 
- `data_source` where the recorded data came from
- `response` participants response to the question 
- `data_value` 
- `low_confidence_limit` the lower bound of the confidence interval 
- `high_confidence-limit` the upper bound of the confidence interval
- `sample_size`
- `break_out`
- `break_out_category`
- `class_id`
- `question_id`
- `location_id`
- `break_out_id`
- `break_out_category_id`
- `response_id`



