---
title:"Data"
output:html_document
---

# Data Cleaning 

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(dplyr)
```

```{r}


#alcohol_data_2007 =
 # read.csv("~/Desktop/finalproject_p8105/website_template/data/PRAM_2007_alcohol.csv")

#tobacco_data_2007 =
 # read.csv("~/Desktop/finalproject_p8105/website_template/data/PRAM_2007_tobacco.csv")

alcohol_data_2007 = read_csv("./data/PRAM_2007_alcohol.csv")

tobacco_data_2007 = read_csv("./data/PRAM_2007_alcohol.csv")
```

Cleaning Alcohol data 

```{r}
cleaned_alc_2007 <- alcohol_data_2007 |>
  janitor::clean_names() |>
  select(-data_value_std_err, -geolocation, -data_value_type)|>
  drop_na(response)

view(cleaned_alc_2007)
```

Cleaning Tobacco Data

```{r}
cleaned_tobac_2007 <- tobacco_data_2007|>
  janitor::clean_names() |>
  select(-data_value_std_err, -geolocation, -data_value_type)|>
  drop_na(response)

view(cleaned_tobac_2007)
```

## Variables 

### Alcohol

- `year`  refers to the year data was recorded
- `class` refers to ....
- `topic` refers to the topic of the data
- `question` the question that was recorded 
- `data_source` where the recorded data came from
- `response` participants response to the question 
- `data_value` 
- `low_confidence_limit` the lower bound of the confidence interval 
- `high_confidence-limit` the upper bound of the confidence interval
- `sample_size`
- `break_out`
- `break_out_category`
- `class_id`
- `question_id`
- `location_id`
- `break_out_id`
- `break_out_category_id`
- `response_id`



